### 2015-06-04 LOI/inc2.tex
setting up the LOI

\end{comment}
\includepdf[pages={1}]{ornl-cover.pdf}
\pagebreak

@@

\underline{\textbf{Executive Summary:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.

@@

\underline{\textbf{Key Technical Contribution:}} The primary contribution of
our research are insights into how to build a hiearchical organization and storage
of massive scientific data sets generated from exascale computations along with 
the necessary information needed for advanced data validation and exploration from 
experimental and observational data. 
We are fundamentally trying to address the fundmantal questions : 1)  How can we 
place and mangage massive scienfici data across all of the tiers of the storage and memory
hiearchy? 2) What are the proper semantics needed in order to help bring knowledge from the applications
to the middleware layer. 3) What information from the storage layer can be exposed to the middleweare such
that the placement of information can be agreed upon from what the application requires and what the
system resources are available.

@@

\underline{\textbf{Significance and Impact:}}
The success of this project will  provide insights into how to build middleware and storage layers which can interact
well with each other, and take user-provided hints. Today data is reduced by application scientist who have 
limited information on what the storage layer can provide. They often make comprimises based on this limited knowledge
and either tune their output for writing or reading performance. This data then gets moved to other locations, and much of
the tuning is lost when the data is read back during their post processing. Furthermore, there is a limited set of operations
which users will be able to stage to other staging nodes for real-tiime-reduction and visualization.

@@

\underline{\textbf{Research Plan:}} 
Our research strategy is to study

\emph{Adaptive Data Management.}

\emph{Proxy Analyses and Workflow Proxies.}

>>>>

\end{comment}
%\includepdf[pages={1}]{ornl-cover.pdf}
%\pagebreak

@@

{\bf Title of Pre-application:} Hierarchal Extreme Scale Knowledge Management \par
{\bf Principal Investigator:} Scott Klasky, Group Leader, ORNL, 854-241-9980, klasky@ornl.gov \par
{\bf Funding Opportunity Announcement Number: DE-FOA-0001338} \par
{\bf List of all co-PIs and Key/Senior Personnel} \par
Hasan Abbasi, Oak Ridge National Laboratory \par
Mark Ainsworth, Oak Ridge National Laboratory JFA, Brown University \par
Matthew Curry, Sandia National Laboratory\par
Jay Lofstead, Sandia National Laboratory \par
Carlos Malzahn, U. Cal. Santa Cruz \par
Manish Parashar, Rutgers University, Oak Ridge National Laboratory \par
Lee Ward, Sandia National Laboratory \par
\vskip 0.2 in

\underline{\textbf{Objective:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.

@@

\underline{\textbf{Key Technical Approach:}} The primary contribution of
our research are insights into how to build a hiearchical organization and storage
of massive scientific data sets generated from exascale computations along with 
the necessary information needed for advanced data validation and exploration from 
experimental and observational data. 
We are fundamentally trying to address the fundmantal questions : 1)  How can we 
place and mangage massive scienfici data across all of the tiers of the storage and memory
hiearchy? 2) What are the proper semantics needed in order to help bring knowledge from the applications
to the middleware layer. 3) What information from the storage layer can be exposed to the middleweare such
that the placement of information can be agreed upon from what the application requires and what the
system resources are available.

@@

The success of this project will  provide insights into how to build middleware and storage layers which can interact
well with each other, and take user-provided hints. Today data is reduced by application scientist who have 
limited information on what the storage layer can provide. They often make comprimises based on this limited knowledge
and either tune their output for writing or reading performance. This data then gets moved to other locations, and much of
the tuning is lost when the data is read back during their post processing. Furthermore, there is a limited set of operations
which users will be able to stage to other staging nodes for real-tiime-reduction and visualization.

@@
